Discrete Quantum Theories and Computing

### 2018-12-01 abstract-ajh1.tex
From: Hanson, Andrew J. <hansona@indiana.edu> Sent: Thursday, November 29, 2018 13:34 To: Tai, Yu-Tsung <yuttai@indiana.edu>; Ortiz, Gerardo <ortizg@indiana.edu>; Sabry, Amr A. <sabry@indiana.edu> Subject: abstract: better last paragraph

Corrections - A. Hanson  29 Nov 2018

@@

Finally, we shift our attention
to consider quantum interval-valued probability measures (IVPMs),
which potentially embody both finite precision measurement and
a sensible correspondence to standard quantum probability.
This interval-valued framework not only provides a natural generalization
of both classical IVPMs and conventional quantum probability measures,
but also establishes bounds on the validity of the Kochen-Specker
and Gleason theorems in realistic experimental environments.

>>>>

Yu-Tsun Tai's abstract:
   Some possible edits - A. Hanson  29 Nov 2018

@@

Finally, we shift our attention
to consider quantum interval-valued probability measures (IVPMs),
which potentially embody both finite precision measurement and
a sensible correspondence to standard quantum probability.
This interval-valued framework not only provides a natural generalization
of both classical IVPMs and conventional quantum probability measures,
but also allows us to establish bounds on the validity of the Kochen-Specker
and Gleason theorems in realistic experimental environments.

### 2018-12-01 dissertation.tex
From: Hanson, Andrew J. <hansona@indiana.edu> Sent: Thursday, November 29, 2018 13:34 To: Tai, Yu-Tsung <yuttai@indiana.edu>; Ortiz, Gerardo <ortizg@indiana.edu>; Sabry, Amr A. <sabry@indiana.edu> Subject: abstract: better last paragraph

Finally, we shift our attention to consider quantum interval-valued
probability measures (IVPMs), which potentially embody both finite
precision measurement and a sensible correspondence to standard quantum
probability. This interval-valued framework not only provides a natural
generalization of both classical IVPMs and conventional quantum probability
measures, but also establishes bounds on the validity of the Kochen-Specker
and Gleason theorems in realistic experimental environments.\end{abstract*}

>>>>

Finally, we shift our attention to consider quantum interval-valued
probability measures (IVPMs), which potentially embody both finite
precision measurement and a sensible correspondence to standard quantum
probability. This interval-valued framework not only provides a natural
generalization of both classical IVPMs and conventional quantum probability
measures, but also allows us to establish bounds on the validity of
the Kochen-Specker and Gleason theorems in realistic experimental
environments.\end{abstract*}
